\documentclass[aspectratio=169]{beamer}

\usepackage[utf8]{inputenc}
\usecolortheme{beaver}
\usepackage{caption}
\usepackage{subcaption}
\usepackage{mathtools}
\usepackage{todonotes}
\usepackage{amsmath}
\usepackage{bm}
\usepackage{listings}
\usepackage{ragged2e}
\usepackage{titlecaps}
\usepackage{fancyvrb}
\def\ci{\perp\!\!\!\!\!\perp}

\newtheorem{proposition}{Proposition}
\Addlcwords{for a is but and with of in as the etc on to if}

\setbeamertemplate{section in toc}{\inserttocsectionnumber.~\inserttocsection}
\usetheme{Boadilla}
\makeatletter
\setbeamertemplate{footline}{%
    \leavevmode%
    \hbox{%
        \begin{beamercolorbox}[wd=.3\paperwidth,ht=2.25ex,dp=1ex,center]{author in head/foot}%
            \usebeamerfont{author in head/foot}\insertshortauthor\expandafter\beamer@ifempty\expandafter{\beamer@shortinstitute}{}{~~(\insertshortinstitute)}
        \end{beamercolorbox}%
        \begin{beamercolorbox}[wd=.55\paperwidth,ht=2.25ex,dp=1ex,center]{title in head/foot}%
            \usebeamerfont{title in head/foot}\insertshorttitle
        \end{beamercolorbox}%
        \begin{beamercolorbox}[wd=.15\paperwidth,ht=2.25ex,dp=1ex,right]{date in head/foot}%
            \usebeamerfont{date in head/foot}\insertshortdate{}\hspace*{2em}
            \insertframenumber{} / \inserttotalframenumber\hspace*{2ex} 
        \end{beamercolorbox}}%
        \vskip0pt%
    }
\makeatother

\begin{document}

\title{Testing and Estimation in Causal Models}
\subtitle{Addressing Mixed and Missing Data Challenges}
\author{Ankur Ankan}
\institute[]{Radboud University, The Netherlands}
\date{}

\maketitle

\begin{frame}{Causal Inference}
	\center{\Large{Many questions in science are causal}}

	\vspace{2em}

	\only<2>{
	\todo[inline]{Insert figure here}

	Epidemiology: Does vaccination reduce the spread of infectious disease?
	}
	\only<3>{
	\todo[inline]{Insert figure here}
	Social Sciences: Does exposure to violent video games increase aggressive behavior in children?
	}
	\only<4>{
	\todo[inline]{Insert figure here}
	Environmental Science: Does deforestation contribute to climate change and loss of biodiversity?
	}
\end{frame}

\begin{frame}{Causal Inference}
	\center{Goal: Understand how an intervention (e.g., deforestation) influences an outcome (e.g., climate change).}

	\vspace{2em}

	\begin{itemize}
		\item \textbf{Understand Causal Relationships: }
			\begin{itemize}
				\item Whether an intervention (e.g., deforestation) impacts the outcome (e.g., climate change).
				\item Examine if the effect is direct, resulting from the intervention alone, or indirect, occurring through intermediary factors.
			\end{itemize}
		\item \textbf{Quantify Causal Relationships: } Measure the magnitude of the intervention's impact. If we increase the deforestation by 2x, how much would climate change.
	\end{itemize}
\end{frame}

\begin{frame}{Randomized Controlled Trial}	
	\center{Best way to answer these causal questions is using \textbf{Randomized Controlled Trials}.}
	\todo[inline]{Insert a figure here}
\end{frame}

\begin{frame}{Randomized Controlled Trial}
	\center{However, randomized controlled trials are \textbf{not always feasible.}}
	
	\vspace{2em}

	\begin{itemize}[<+->]
		\item \textbf{Impossible to create two groups: } We cannot create a copy of earth on which to apply the intervention.
		\item \textbf{Unethical: } Can't give some treatment to a patient.
		\item \textbf{Expensive: }
	\end{itemize}

	\vspace{2em}

\only<4>{
\center{Can we answer these questions using data that we already have (i.e., observational data)?}}
\end{frame}

\begin{frame}{Causal Graphs}
	\center{Yes, but we need an understanding of the causal mechanism}

	\todo[inline]{Show an example of a DAG. Show causal paths, and causal effects.}

	\todo[inline]{Highlight what the two tasks outlined before mean in terms of Causal Graphs}
	\begin{itemize}
		\item Causal relationship $ \implies $ causal paths.
		\item Quantification $ \implies $ Strength of these edges.
	\end{itemize}
\end{frame}

\begin{frame}{Mixed and Missing Data}
	\center{I have focused on improving these methods for mixed and missing data.}

	\textbf{Mixed Data:}
		\begin{enumerate}
			\item Numerical:
			\item Categorical:
			\item Ordinal:
		\end{enumerate}

	\textbf{Missing Data:} Not all variables can be measured. For example climate change.
\end{frame}

\begin{frame}{Constructing Causal Graphs}
	\center{How do we construct causal graphs: Usually done manually based on knowledge}
	\center{How do we know our graph is correct?: Model Testing}
	
	Graph $ \implies $ Independence statements.
	Independence means 
\end{frame}

\begin{frame}{Testing Casual Graphs}
	Selecting the correct conditional independence test depends on a lot of factors.

	In one of the chapters, we presented a practical guide for researchers trying to apply these methods in their research on how to carry out this testing.
\end{frame}

\begin{frame}{Conditional Independence Tests}
	Model testing relies on these statistical Conditional independence tests.
	Conditional Independence tests can also be used for constructing these graphs
	automatically.

	Hence, important that these tests are accurate.
\end{frame}

\begin{frame}{Chapter 3: CI test for testing and constructing graph}
	The model testing utilizes conditional independence tests.

	In Chapter 3, we propose a novel test for mixed data.
\end{frame}

\begin{frame}{Causal Effect Estimation}
	Some of the variables are unobserved.
	Impossible to estimate the effect.
	Trick: Use an observed child of the variable to estimate it by fixing one of the
	variables.
\end{frame}

\begin{frame}{Software}
	To make it easy for these methods to use, we have a software package.
\end{frame}

\begin{frame}{Future research}
\end{frame}

\begin{frame}
	\Huge{Thank you}
\end{frame}

\end{document}
